---
title: "coi5p-vignette"
author: "Cameron M. Nugent"
data: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{coi5p-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Once completed can - submit it to the Journal of Statistical Software or The R Journal. Online, R journals that are peer reviewed. The BOLD special issue is the first option.


This of this from a beginners perspective, use simple and accesible language as may be used by international researchers. goal is clear and accesible.
 - Modify this to explain/showcase the code and how it works
 - use `ctrl-shift-k` to knit the vignette and preview the output.
 
What this file will need to include:
 - a basic example of getting a string loaded into coi5p
 - how the different functions of the package are run, what they result in
 - explination as to why the functions are split - save user time b/c if you just want it in frame and not translated, that is possible!
 - show how this could be integrated into a workflow.
 
 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(coi5p)
```
